### 2011-02-03 docs/architecture/architecture.tex
updates to the directory structure discussion

 Important subdirectories include:
 \begin{itemize}
 \item {\tt constants/}

@@

@@

   Each problem in MAESTRO gets it own subdirectory.  The {\tt
   GNUmakefile} includes the instructions on how to build the
   executable, including what modules in {\tt extern} are used.

   Any file that you place in a sub-directory here takes 
   precedence over a file of the same name in {\tt MAESTRO/}.
   This allows problems to have custom versions of the main
   MAESTRO routines (e.g.\ initial conditions via {\tt initdata.f90}.
   See \S~\ref{sec:makefile} for details on the build system.

>>>>

 Important subdirectories include:
 \begin{itemize}
 \item {\tt conductivity/}

 Various routines for computing the thermal conductivity used in the
 thermal diffusion part of the algorithm.

 \item {\tt constants/}

@@

 \item {\tt model\_parser/}

 A simple Fortran module for reading in 1-d initial model files.  This
 is used by the initialization routines to get the initial model data.

@@

   Each problem in MAESTRO gets it own subdirectory.  The {\tt
     GNUmakefile} in the problem directory includes the instructions
   on how to build the executable, including what modules in {\tt
     extern} are used.

   Any file that you place in a sub-directory here takes 
   precedence over a file of the same name in {\tt MAESTRO/}.
   This allows problems to have custom versions of the main
   MAESTRO routines (e.g.\ initial conditions via {\tt initdata.f90}.
   See \S~\ref{sec:makefile} for details on the build system).
